\documentclass{resume}
\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins

\name{Bryce P Mazurowski, PhD} % Your name
% NOTE: I don't want to post my number on GitHub
\address{33 West Ontario Street, Apt 25A \\ Chicago, IL 60654} % Your address
\address{(585) 519-9511 \\ brycepm2@gmail.com} % Your phone number and email

\begin{document}
\vspace{0.5in}
Dear Planet Hiring Team,

While browsing Planet's website, I noticed the opening for a Senior
Software Engineer in the Orbit R\&D Group.
%
Seeing this role and the expected impact was exciting.
%
Over the course of my MS and PhD studies at the University of Illinois
Urbana-Champaign, I have been developing engineering software in C++.
%
Scientific computing is an area I am passionate about and a career
path I plan to follow.
%
Working on orbital mechanics software for Planet's extensive fleet of
satellites would be a a great opportunity to continue to develop my
physics-based software development skills.
%

I have greatly enjoyed my time learning and creating at the University
of Illinois.
%
The work has been an engaging mix of reading papers, thinking through
problems, writing out the math, planning out algorithms, and
implementing them.
%
All of the implementation is done in a C++ codebase that
is used by many collaborators, where the ability to communicate
is a necessity. 
%
While I have spent plenty of time focusing on the math and physics
that apply to the problems I study, I have also put significant effort
into writing clean, safe and efficient software.
%
Our research group made uses Git for version control and maintains a
large suite of tests for quality assurance that are run automatically.
%
We also regularly containerize and share our code with collaborators
to use on machines of their choice.
%
I have been operating in a research-heavy role remotely for
several years now, which is another exciting aspect of this position.
%

My research background is in the development of numerical analysis
methods for solid mechanics problems.
%
In particular, I worked to develop finite element method software and
associated pre and post-processing subroutines.
%
While my degree is out of the Civil Engineering department, all of my
research has been motivated by the aerospace industry.
%
The main application being hypersonic aircraft, which stand to
play a major role in space operations through single stage to orbit
launch vehicles.
%
While the finished product of my work is compiled into several journal
papers and conference presentations, my favorite part is pen-on-paper math
and commits sent to our git repository.
%

Orbital mechanics is an application area that really excites me.
%
While Chicago doesn't have the best night sky I get out with my
telescope as often as possible to catch an up-close glimpse of planets
and moons.
%
Sometimes I have to settle with Stellarium on my laptop, but getting a
glimpse either way is exciting.
%
I would be ecstatic to try and catch a glimpse of a satellite I had a
hand in maneuvering up there.
%

Planet's work in Earth imagery is unlocking a level of detail that
is unmatched.
%
The data and insights are invaluable, and the company acts on strong
principles.
%
The effort put in to capture the situation in Ukraine and monitor
related military and economic activity are admirable.
%
I would be very happy to contribute to a key part of Planet's
technology stack, and I have a great skillset to make a difference.
%


My passion and skill set align with Planet's mission to develop
to keep an organized and effective fleet of satellites in space.
%
My experience and proven ability to perform develop scientific software
make this a position I would excel in.
%
I would appreciate the opportunity to explore this opening further with you.
%


Sincerely,

Bryce Mazurowski
\end{document}
